---
title: "DecisionTreeProgram"
author: "Mohammad Tariq"
date: "May 21, 2018"
output: 
  html_document:
    css: mystyle.css
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Markdown

R use **party** package to create decision trees. And in party package there is inbuilt dataset named as **readingSkills** on which we will create decision tree. we can get to know about datasets present in a particular package by executing the following R code
```{r  include=FALSE}
library(party)
```

```{r}
  data(package='party')
```
The **party** package has the function called as **ctree** to create and analyzed tree.
The dataset **readingSkills** has the attributes age,score,shoeSize and the Class varibale nativeSpeaker. Decision tree will describe that whether a person is a ntiveSpeaker or not by analyzing age,score and shoesize attributes.

## Input data readingSkills 
The following data is the sample of readingSkills dataset
```{r, echo=FALSE}
writeLines("td, th { padding : 6px } th { background-color : #000000 ; color : white; border : 1px solid white; } td { color : black ; border : 1px solid gray }", con = "mystyle.css")

knitr::kable(readingSkills[1:20, ],format="html")
```

Assigning first 100 rows of readingSkills dataset to a varaiable. And lets just named variable  training.Data 

```{r }
training.Data<-readingSkills[c(1:110), ]
```

Now we will create decision tree using **ctree()** function.
```{r}
decision.tree<- ctree(
  nativeSpeaker ~ age + shoeSize + score, data = training.Data
)
```










## Decision Tree 

```{r}
plot(decision.tree)
```

## Conclusion
From above tree we can conclude that 

- A person whose readingSkills Score is greater than 50.84 is a nativeSpeaker.
- A person whose score is greater than 34.72 and age is less than or equal to 7 is also a nativeSpeaker.
